\documentclass[12pt]{article}
\input{physics2}
\begin{document}

\section*{NYU Physics 2---Problem Set 12}

Due Friday 2020 May 8 by midnight NYC time.

\paragraph{Problem~\theproblem:}\refstepcounter{problem}\label{prob:wave}%
In class we considered a plane-parallel sinusoidal wave of the form
\begin{align}
  \vec{E} &= E_0\,\hat{x}\,\cos(k\,z - \omega t) \\
  \vec{B} &= B_0\,\hat{y}\,\cos(k\,z - \omega t) \quad ,
\end{align}
where $E_0$ and $B_0$ are amplitudes, $k$ is the magnitude of a
wave number, and $\omega$ is an angular frequency.
The $y$ component of the Maxwell's equation involving
$\curl{\vec{E}}$ in vacuum is
\begin{align}
  \frac{\dd}{\dd z}E_x - \frac{\dd}{\dd x}E_z = -\frac{\dd}{\dd t}B_y
  \quad ,
\end{align}
and the $x$ component of the equation involving $\curl{\vec{B}}$ is
\begin{align}
  \frac{\dd}{\dd y}B_z - \frac{\dd}{\dd z}B_y = \mu_0\,\epsilon_0\,\frac{\dd}{\dd t}E_x
  \quad .
\end{align}
Show---by taking the derivatives and plugging in---that the given forms
for the electric and magnetic fields can
satisfy these equations, provided that there is some particular relationship
between $E_0$ and $B_0$ and some particular relationship between $k$ and $\omega$.
What are those relationships?

You should be able to write an
expression for the ratio $E_0/B_0$ and an expression for the ratio $\omega/k$.
Both of these expressions should depend only on fundamental constants
$\mu_0$, $\epsilon_0$, and $c$.

\paragraph{Problem~\theproblem:}\refstepcounter{problem}%
In different wavelength regions, physicists tend to use different
units to describe photons. Make a table giving the wavelength
$\lambda$, wave number $k$, frequency $f$, angular frequency $\omega$,
and energy $E$ of each of the following photons:
\begin{itemize}
\item a radio wave at $f=70\,\GHz$ detected by ESA \textsl{Planck}
\item an infrared photon at $\lambda=10\,\mum$ emitted by Earth to space
\item a blue photon at $\lambda=410\,\nm$ absorbed by a leaf in photosynthesis
\item an x-ray at $E=1.02\,\MeV$ emitted by electron--positron annihilation
\end{itemize}
For the energies $E$ you will have to use that a photon has energy $E=h\,f$
where $h$ is the Planck constant. Give your answers in SI units except for the
energies, which you should give in $\eV$.

\paragraph{Problem~\theproblem:}\refstepcounter{problem}%
Put yourself inside a parallel-plate capacitor with plate radius $a$
and plate separation $h\ll a$. Now imagine that there is current $I$
going in to the capacitor, so it is charging, with the top plate having
positive charge $Q>0$ and $I = \dd Q/\dd t > 0$. What are the directions
of the electric and magnetic fields at or near the edge of the capacitor
(at $r\sim a$)? Which way does the Poynting vector point?

Now consider the case of negative current, such that $Q>0$ and $\dd
Q/\dd t<0$. Which way does the Poynting vector point?

Now consider the two cases of negative charge, so consider $Q<0$ and
$\dd Q/\dd t>0$ and $Q<0$ and $\dd Q/\dd t<0$. Summarize your answers
in a chart: What is the direction of the Poynting vector for every
choice of the sign of $Q$ and the sign of $\dd Q/\dd t$?

\paragraph{Problem~\theproblem:}\refstepcounter{problem}%
An electromagnetic wave carries energy and momentum. If you take the
wave form given above in Problem~\ref{prob:wave}, what are the mean
values of $E^2\equiv\vec{E}\cdot\vec{E}$ and
$B^2\equiv\vec{B}\cdot\vec{B}$ in the wave? Take your mean over space at
a fixed time, or take your mean over time at fixed space, or equivalent!

Look up the formulae for energy density
in the electromagnetic fields. What are the mean electric and magnetic energy densities
in the wave? Use your relationships between $E_0$ and $B_0$ to give
your answers just in terms of $E_0$ and physical constants.

For electromagnetic waves, the momentum density is just the energy density
divided by the speed of light. What is the momentum density and in which
direction do you think it points?

\end{document}
