\documentclass[12pt]{article}
\input{physics2}
\begin{document}

\section*{NYU Physics 2---Problem Set 10}

Due Thursday 2022 April 21 by 12:30\,pm on Brightspace.

\startproblem%
In lecture on 2022-04-07 we considered a very simple circuit that consisted only
of a capacitor $C$ and an inductor $L$ (we imagined $R\rightarrow 0$).
We showed that this circuit creates a differential equation whose solutions
are sines and cosines.
Imagine that the charge $Q$ on the capacitor is varying with time like
\begin{equation}
  Q(t) = Q_0\,\cos(\omega_0\,t) ~,
\end{equation}
where $\omega_0 = 1/\sqrt{LC}$.
Now remind yourself of (or look up) the energy stored in a capacitor, and the energy
stored in an inductor, and plot these two energies vs time, on the same graph.
Be sure to mark your graph with the amplitude of each curve, and the period and anything
else you think might be relevant.
Plot also the total energy (energy in capacitor plus energy in inductor).

\textsl{Note:} To do this problem you will have to take the derivative of $Q(t)$ to get
$I(t)$; recall that in our sign convention for this problem, $I(t)=-\dd Q/\dd t$.

\textsl{Hint:} If everything goes well in this problem, you will find yourself using the fact that $\sin^2\theta + \cos^2\theta = 1$.

\startproblem%
Look at the AC circuit we discussed in Lecture on
2022-04-12, which had an AC generator $V,\omega$, a resistor $R$,
a capacitor $C$, and an inductor $L$, all in parallel.
The AC generator produces a time-dependent voltage
\begin{equation}
  V(t) = V_0\,\cos(\omega\,t) = \Re\left\{V_0\,\exp(i\,\omega\,t)\right\} ~,
\end{equation}
and it led to sinusoidally varying currents $I_R(t), I_C(t), I_L(t)$ in each of the three
parallel legs, some of which had $\cos(\omega\,t)$ and some of which had
$\sin(\omega\,t)$ dependence.
State a clear argument that each of these currents can be expressed in the
form
\begin{equation}
  I(t) = \Re\left\{\frac{V_0}{Z}\,\exp(i\,\omega\,t)\right\} ~,
\end{equation}
if we we associate an impedance to each of the circuit elements as follows:
\begin{align}
  Z_R &= R \\
  Z_C &= \frac{1}{i\,\omega\,C} \\
  Z_L &= i\,\omega\,L ~.
\end{align}
At some point you might need to use the facts $i^2 = -1$ and $1/i = -i$. Or not!

\startproblem%
If you have an inductor $L$ and a capacitor $C$ in series, what does
the total complex impedance $Z$ approach as $\omega\rightarrow
(L\,C)^{-1/2}$? If you have the same two elements in parallel, what
does the total complex impedance approach in this same limit?

Now imagine that associated with the inductor $L$ there is a
resistance $R$. That is, there is always a small resistance $R$ in
series with the inductor, in both cases. Now what do your two limits
become?

\textsl{Note:} To solve this problem you will have to use the fact that
complex impedances add in series in parallel the way resistances do, but
in complex math.

%% % I'm just not going to do this problem this year.
%% \startproblem%
%% In Lecture on 2020-04-16 we found, in the complex formalism, that for
%% an LRC circuit driven by an AC voltage source producing amplitude $V$ and frequency $\omega$, the current flowing in the
%% circuit is
%% \begin{equation}\label{eq:res}
%%   I = \frac{V}{R + i\,\left(\omega\,L - \frac{1}{\omega\,C}\right)}\,\exp(i\,\omega\,t)
%%   \quad .
%% \end{equation}
%% Plot the amplitude (the magnitude of the complex prefactor in front of
%% the exponential) of this current as a function of frequency
%% $\omega$. Be sure to label the plot with the maximum value, the limit
%% at $\omega\rightarrow 0$, and the asymptotic limit at
%% $\omega\rightarrow\infty$.

\startproblem%
Here's a dumb model of an FM radio receiver circuit: It is a circuit that has a
resonance (big current $I$ given driving voltage $V$) at the radio-station
carrier frequency $f$, but very little response (small current given
driving voltage) at the carrier frequency of other nearby radio stations.
Assume that the response is given by something like
\begin{equation}\label{eq:res}
  I = \frac{V}{R + i\,\left(\omega\,L - \frac{1}{\omega\,C}\right)}\,\exp(i\,\omega\,t) ~,
\end{equation}
which is an equation that appears in the reading for a resonant circuit.
What do you need to be true about $R$, $L$,
and $C$ for a radio to be tuned to the frequency of The Beat of New
York KTU at 103.5 (what units are those?),
but have less than 10-percent as much
response to a pirate radio station operating at 103.7? Assume, for
definiteness, that these two stations are impinging on the radio with
the same voltage amplitude $V$.

You are going to get one relationship between $L$ and
$C$ to ensure that the radio is tuned to 103.5, and then there is a
relationship also involving $R$ to ensure that the radio is
insensitive to 103.7.

\textsl{Notes:} Be careful with your units! Also, frequencies are in Hz
(cycles per second) but the equation above uses $\omega$ (radians per second).

\end{document}
